Article title

### 2017-08-02 paper-webserver.tex
ADD: initial synth of outline from chad

\section{Introduction}
Broad --> narrow
-Bacterial infections are a cause of human disease -> associated costs
-Surveillance is used to monitor known pathogens and detect emerging threats, to lower burden of human illness
-Until recently, surveillance involved traditional reference laboratory techniques (and still does) --> examples of both old and new (WGS), what they measure, how they are used
-WGS methods have great potential, but some drawbacks (list with references)
-Some of the drawbacks can be solved by providing pre-computed analyses for routine tasks
-We have previously created SuperPhy, which helps solve some of the issues
-Some issues still remain
-In this study, we have addressed these issues by ... which will provide these benefits

>>>>

\section{Introduction}
% new outline
% para
% 1. brief: WGS is standard
% 2. Big Problem: but tools are for individual analysis
% 3. 100,000 genomes, (lookup number for Enterobase, GenBank), how do we run analysis on it
% 4. previous methods (Galaxy/IRIDA: real-time, but no storage of results, other website examples - Denmark?), what problems they addressed
% 5. Problems that remain / lack of result storage means: recomputation, lost data, can't reference old analyses, not suited for "big data"
% 6. Solutions in general: store and increment, huga "big data" analyses, parallelization /queues
% para
% 1. Our specific problem, previous work
% 2. Why solving it is important (for Public health / research)
% 3. how we solved it
% para
% 4. benefits: rapid analyses in real-time -> huge comparisons, replace reference labs -> time & money saved, future work -> expand analyses, more genomes, more species
% 5. analyses modules -> conda -> IRIDA/Galaxy
% 6. short snippit on website link & github link
